---
title: "Final assigment"
author: "Marco Antonio Béjar Villalba"
date: "5/2/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(maddison)
library(dplyr)
library(maddison)
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions
This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

[Link to slide](https://rpubs.com/marco-antonio-bejar-villalba/721903)

[Link to app](https://marco-antonio-bejar-villalba.shinyapps.io/assigment/)

[Link to github](https://github.com/marco-antonio-bejar-villalba/ShinyApplication)

## Data

This app uses the madisson data set to show the GDP per capita of many countries.

Will use only a few countries in order to have a short code that can be reviewed easily.

The app has only two controls, one for the country and another for the date.

The date control is a slider, you can select the dates in interval and with the other
control you can select among some few countries.

## Cleaning

I use the folowing code to clean the data.

```{r cars, echo = TRUE}
data("maddison")
plotCountry<-function(aCountry="Austria",fromYear="1950",toYear="2010"){
  fromYearasDate=as.Date(paste(fromYear,"-01-01",sep=""))
  toYearasDate=as.Date(paste(toYear,"-01-01",sep=""))
  dataFiltered<-filter(maddison,
                       !is.null(gdp_pc),
                       country==aCountry,
                       year>fromYearasDate,
                       year<toYearasDate)
  plot(dataFiltered$year,dataFiltered$gdp_pc, type="l")
}
```

## Slide with Plot

Here an example
```{r pressure}
plotCountry()
```

